Meta-analysis of the Interoceptive Accuracy Scale

### 2024-02-26 analysis/study2.qmd
update study 2

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_cfa7 <- vars_cfa[vars_cfa != "CoughSneeze"]

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BPCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAIT, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS,PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10n)  # BDI, STAI, PHQ4
```

@@

@@

@@

### Body

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
names(df2)  # BPQ_R_Supra and _Sub?
names(df3)
names(df4)  # individual items 1-26
names(df7b)  # BPQ sum
names(df8a)  # individual items

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
)
```

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |>  -->
<!--     mutate(var_Correlate = "Attention Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Body Listening"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Emotional Awareness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Distracting"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Noticing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Worrying"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Self Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Trusting") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # names(df3)[str_detect(names(df3), "TAS")] -->
<!-- # names(df4b)[str_starts(names(df4b), "TAS")] -->

<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |>  -->
<!--     mutate(var_Correlate = "External Thinking"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Mood -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"), -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-9)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-4)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (PHQ-4)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (BDI-II)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (STAI-5)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Boderline Personality") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Psychopathology -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Antagonism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Detachment"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Disinhibition"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Negative Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Psychoticism") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Constricted Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Eccentric"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Magical Thinking"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "No Close Friends"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Odd Speech"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Reference"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Social Anxiety"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Suspiciousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Unusual Perceptions") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #  names(select(df5a, starts_with("ASQ"))) -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |>  -->
<!--     mutate(var_Correlate = "Imagination"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Lack of Social Skills"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Low Attentional Switching"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Patterns and Numbers"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Routines") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Personality -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |>  -->
<!--     mutate(var_Correlate = "Agreeableness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Conscientiousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |> -->
<!--     mutate(var_Correlate = "Neuroticism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Openness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |> -->
<!--     mutate(var_Correlate = "Extraversion"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |> -->
<!--     mutate(var_Correlate = "Honesty-Humility") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Alive", component="World Beliefs") |>  -->
<!--     mutate(var_Correlate = "Alive"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Changing", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Changing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Enticing", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Enticing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Good", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Good"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Hierarchical", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Hierarchical"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PI_Safe", component="World Beliefs") |> -->
<!--     mutate(var_Correlate = "Safe") -->
<!--   # TODO: Add understanble -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>  -->
<!--     mutate(var_Correlate = "Extraterrestrial"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Global Conspiracies"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Government Malfeasance"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Information Control"), -->
<!--   make_cor(df5a, vars_cfa7, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |> -->
<!--     mutate(var_Correlate = "Personal Wellbeing") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Ability", component="Lying Profile") |>  -->
<!--     mutate(var_Correlate = "Ability"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Frequency", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Frequency"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Contextuality", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Contextuality"), -->
<!--   make_cor(df5a, vars_cfa7, with = "LIE_Negativity", component="Lying Profile") |> -->
<!--     mutate(var_Correlate = "Negativity") -->
<!-- ) -->
<!-- ``` -->

### Summary

>>>>

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_intero <- vars_cfa[vars_cfa != "CoughSneeze"]

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ (?), TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ (?), BPQ, MAIA, BRS (resilience?), PBCS (private bodily consciousness?)
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
```

@@

### Gender

@@

### Age

@@

## Body

### MAIA

```{r}
names(df2)[str_detect(names(df2), "MAIA")]  
names(df4)[str_detect(names(df4), "MAIA")]  # ?
names(df7a)[str_detect(names(df7a), "MAIA")]  
names(df7b)[str_detect(names(df7b), "maia")] 
names(df10a)[str_detect(names(df10b), "MAIA")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  # df4
  # df7a
  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df7b
  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df10a
  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting")
)
```

### BPQ

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
names(df3)[str_detect(names(df3), "BPQ")]  
names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "BPQ_A", component="BPQ") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="BPQ") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="BPQ") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="BPQ") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
)
```

### Alexithymia

```{r}
names(df2)[str_detect(names(df2), "TAS")]
names(df3)[str_starts(names(df3), "TAS")]
names(df7c)[str_starts(names(df7c), "TAS")]
names(df8b)[str_starts(names(df8b), "TAS")]

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)
```

## Mood

### Depression

```{r}
names(df6)[str_detect(names(df6), "PHQ")] 
names(df7b)[str_detect(names(df7b), "PHQ")]
names(df7c)[str_detect(names(df7c), "BDI")]
names(df8b)[str_detect(names(df8b), "PHQ")]
names(df9)

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)")
)
```

### Anxiety

```{r}
names(df6)[str_detect(names(df6), "GAD")] 
names(df7a)[str_detect(names(df7a), "STAI")] 
names(df7b)[str_detect(names(df7b), "STAI")] 
names(df7c)[str_detect(names(df7c), "STAI")]

data <- rbind(
  data,
  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)")
)
```

## Psychopathology

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
    mutate(var_Correlate = "Boderline Personality")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "PID5_Antagonism", component="Maladaptive") |>
    mutate(var_Correlate = "Antagonism"),
  make_cor(df10a, vars_intero, with = "PID5_Detachment", component="Maladaptive") |>
    mutate(var_Correlate = "Detachment"),
  make_cor(df10a, vars_intero, with = "PID5_Disinhibition", component="Maladaptive") |>
    mutate(var_Correlate = "Disinhibition"),
  make_cor(df10a, vars_intero, with = "PID5_NegativeAffect", component="Maladaptive") |>
    mutate(var_Correlate = "Negative Affect"),
  make_cor(df10a, vars_intero, with = "PID5_Psychoticism", component="Maladaptive") |>
    mutate(var_Correlate = "Psychoticism")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>
    mutate(var_Correlate = "Constricted Affect"),
  make_cor(df10a, vars_intero, with = "SPQ_Eccentric", component="Schizotypic") |>
    mutate(var_Correlate = "Eccentric"),
  make_cor(df10a, vars_intero, with = "SPQ_MagicalThinking", component="Schizotypic") |>
    mutate(var_Correlate = "Magical Thinking"),
  make_cor(df10a, vars_intero, with = "SPQ_NoCloseFriends", component="Schizotypic") |>
    mutate(var_Correlate = "No Close Friends"),
  make_cor(df10a, vars_intero, with = "SPQ_OddSpeech", component="Schizotypic") |>
    mutate(var_Correlate = "Odd Speech"),
  make_cor(df10a, vars_intero, with = "SPQ_Reference", component="Schizotypic") |>
    mutate(var_Correlate = "Reference"),
  make_cor(df10a, vars_intero, with = "SPQ_SocialAnxiety", component="Schizotypic") |>
    mutate(var_Correlate = "Social Anxiety"),
  make_cor(df10a, vars_intero, with = "SPQ_Suspiciousness", component="Schizotypic") |>
    mutate(var_Correlate = "Suspiciousness"),
  make_cor(df10a, vars_intero, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>
    mutate(var_Correlate = "Unusual Perceptions")
)
```

```{r}
#  names(select(df10a, starts_with("ASQ")))
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "ASQ_Imagination", component="Autistic") |>
    mutate(var_Correlate = "Imagination"),
  make_cor(df10a, vars_intero, with = "ASQ_LackSocialSkills", component="Autistic") |>
    mutate(var_Correlate = "Lack of Social Skills"),
  make_cor(df10a, vars_intero, with = "ASQ_LowAttentionalSwitching", component="Autistic") |>
    mutate(var_Correlate = "Low Attentional Switching"),
  make_cor(df10a, vars_intero, with = "ASQ_Patterns", component="Autistic") |>
    mutate(var_Correlate = "Patterns and Numbers"),
  make_cor(df10a, vars_intero, with = "ASQ_Routine", component="Autistic") |>
    mutate(var_Correlate = "Routines")
)
```

## Personality

```{r}
names(df7a)[str_detect(names(df7a), "NEO")]
names(df9)[str_detect(names(df9), "BFI_")]

data <- rbind(
  data,
  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
    mutate(var_Correlate = "Honesty-Humility")
)
```

## Others

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "PI_Alive", component="World Beliefs") |>
    mutate(var_Correlate = "Alive"),
  make_cor(df10a, vars_intero, with = "PI_Changing", component="World Beliefs") |>
    mutate(var_Correlate = "Changing"),
  make_cor(df10a, vars_intero, with = "PI_Enticing", component="World Beliefs") |>
    mutate(var_Correlate = "Enticing"),
  make_cor(df10a, vars_intero, with = "PI_Good", component="World Beliefs") |>
    mutate(var_Correlate = "Good"),
  make_cor(df10a, vars_intero, with = "PI_Hierarchical", component="World Beliefs") |>
    mutate(var_Correlate = "Hierarchical"),
  make_cor(df10a, vars_intero, with = "PI_Safe", component="World Beliefs") |>
    mutate(var_Correlate = "Safe"),
  make_cor(df10a, vars_intero, with = "PI_Understandable", component="World Beliefs") |>
    mutate(var_Correlate = "Understandable")
)
```

```{r}
data <- rbind(
  data,
  make_cor(df10a, vars_intero, with = "GCBS_Extraterrestrial", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Extraterrestrial"),
  make_cor(df10a, vars_intero, with = "GCBS_GlobalConspiracies", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Global Conspiracies"),
  make_cor(df10a, vars_intero, with = "GCBS_GovernmentMalfeasance", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Government Malfeasance"),
  make_cor(df10a, vars_intero, with = "GCBS_InformationControl", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Information Control"),
  make_cor(df10a, vars_intero, with = "GCBS_PersonalWellbeing", component="Conspiracy Beliefs") |>
    mutate(var_Correlate = "Personal Wellbeing")
)
```
